Clean data

### 2018-03-15 01_clean-data.Rmd
Make conditions factors

results <- results_raw %>%
  # Only select necessary columns
  select(id = ResponseId, duration = `Duration (in seconds)`,
         start_date = StartDate, end_date = EndDate,
         crackdown, issue, funding, starts_with("Q")) %>%
  rename(favor_humanitarian = Q2.1_1, favor_human_rights = Q2.1_2, 
         favor_development = Q2.1_3, donate_likely = Q2.3, 
         amount_donate = Q2.4_1, amount_keep = Q2.4_2, amount_why = Q2.5,
         give_charity = Q3.2, volunteer = Q3.3, political_knowledge = Q3.4,
         ideology = Q3.5, education = Q3.6, religiosity = Q3.7,
         gender = Q3.9, gender_other = Q3.9_4_TEXT, income = Q3.10, age = Q3.11) %>%
  # Clean up experimental condition columns
  mutate(issue = recode(issue, `human rights for refugees` = "Human rights",
                        `humanitarian assistance for refugees` = "Humanitarian assistance"),
         funding = recode(funding, `government donors` = "Government",
                          `individual, private donors` = "Private")) %>%
  mutate(crackdown = ifelse(str_detect(crackdown, "harshly restrict"), 
                            "Crackdown", "No crackdown")) %>% 
  # Attention checks
  mutate(attention1_correct = str_split(Q1.3, ",") %>% 
           map_lgl(~ all(attention1_answer %in% .) & length(.) == length(attention1_answer)),
         attention2_correct = Q3.8 == attention2_answer) %>% 
  # Factorize variables
  mutate(donate_likely = factor(donate_likely, levels = likelihood, ordered = TRUE)) %>% 
  mutate_at(vars(favor_humanitarian, favor_human_rights, favor_development),
            funs(factor(., levels = favorability, ordered = TRUE))) %>% 
  mutate(give_charity = factor(give_charity, 
                               levels = frequency_charity, ordered = TRUE),
         political_knowledge = factor(political_knowledge, 
                                      levels = frequency_public_affairs, ordered = TRUE),
         ideology = factor(ideology, levels = levels_ideology, ordered = TRUE),
         education = factor(education, levels = levels_education, ordered = TRUE),
         religiosity = factor(religiosity, levels = frequency_religion, ordered = TRUE),
         gender = recode(gender, `Other:` = "Other"),
         gender = factor(gender, levels = levels_gender, ordered = TRUE),
         income = factor(income, levels = levels_income, ordered = TRUE),
         age = factor(age, levels = levels_age, ordered = TRUE),
         check1 = factor(attention1_correct, levels = c(TRUE, FALSE),
                         labels = levels_attention, ordered = TRUE),
         check2 = factor(attention2_correct, levels = c(TRUE, FALSE),
                         labels = levels_attention, ordered = TRUE)) %>% 
  # Dichotomize variables
  mutate(donate_likely_bin = fct_recode(donate_likely,
                                        `Not likely` = "Extremely unlikely",
                                        `Not likely` = "Somewhat unlikely",
                                        `Not likely` = "Neither likely nor unlikely",
                                        Likely = "Somewhat likely",
                                        Likely = "Extremely likely")) %>% 
  mutate_at(vars(favor_humanitarian, favor_human_rights, favor_development),
            funs(bin = fct_recode(., 
                                  `Not favorable` = "Very unfavorable",
                                  `Not favorable` = "Unfavorable",
                                  `Not favorable` = "Neutral",
                                  Favorable = "Favorable",
                                  Favorable = "Very favorable")))

>>>>

results <- results_raw %>%
  # Only select necessary columns
  select(id = ResponseId, duration = `Duration (in seconds)`,
         start_date = StartDate, end_date = EndDate,
         crackdown, issue, funding, starts_with("Q")) %>%
  rename(favor_humanitarian = Q2.1_1, favor_human_rights = Q2.1_2, 
         favor_development = Q2.1_3, donate_likely = Q2.3, 
         amount_donate = Q2.4_1, amount_keep = Q2.4_2, amount_why = Q2.5,
         give_charity = Q3.2, volunteer = Q3.3, political_knowledge = Q3.4,
         ideology = Q3.5, education = Q3.6, religiosity = Q3.7,
         gender = Q3.9, gender_other = Q3.9_4_TEXT, income = Q3.10, age = Q3.11) %>%
  # Clean up experimental condition columns
  mutate(issue = recode(issue, `human rights for refugees` = "Human rights",
                        `humanitarian assistance for refugees` = "Humanitarian assistance"),
         funding = recode(funding, `government donors` = "Government",
                          `individual, private donors` = "Private")) %>%
  mutate(crackdown = ifelse(str_detect(crackdown, "harshly restrict"), 
                            "Crackdown", "No crackdown")) %>% 
  mutate(crackdown = factor(crackdown, levels = c("No crackdown", "Crackdown"), 
                            ordered = TRUE),
         issue = factor(issue, levels = c("Human rights", "Humanitarian assistance"), 
                        ordered = TRUE),
         funding = factor(funding, levels = c("Government", "Private"), 
                          ordered = TRUE)) %>% 
  # Attention checks
  mutate(attention1_correct = str_split(Q1.3, ",") %>% 
           map_lgl(~ all(attention1_answer %in% .) & length(.) == length(attention1_answer)),
         attention2_correct = Q3.8 == attention2_answer) %>% 
  # Factorize variables
  mutate(donate_likely = factor(donate_likely, levels = likelihood, ordered = TRUE)) %>% 
  mutate_at(vars(favor_humanitarian, favor_human_rights, favor_development),
            funs(factor(., levels = favorability, ordered = TRUE))) %>% 
  mutate(give_charity = factor(give_charity, 
                               levels = frequency_charity, ordered = TRUE),
         political_knowledge = factor(political_knowledge, 
                                      levels = frequency_public_affairs, ordered = TRUE),
         ideology = factor(ideology, levels = levels_ideology, ordered = TRUE),
         education = factor(education, levels = levels_education, ordered = TRUE),
         religiosity = factor(religiosity, levels = frequency_religion, ordered = TRUE),
         gender = recode(gender, `Other:` = "Other"),
         gender = factor(gender, levels = levels_gender, ordered = TRUE),
         income = factor(income, levels = levels_income, ordered = TRUE),
         age = factor(age, levels = levels_age, ordered = TRUE),
         check1 = factor(attention1_correct, levels = c(TRUE, FALSE),
                         labels = levels_attention, ordered = TRUE),
         check2 = factor(attention2_correct, levels = c(TRUE, FALSE),
                         labels = levels_attention, ordered = TRUE)) %>% 
  # Dichotomize variables
  mutate(donate_likely_bin = fct_recode(donate_likely,
                                        `Not likely` = "Extremely unlikely",
                                        `Not likely` = "Somewhat unlikely",
                                        `Not likely` = "Neither likely nor unlikely",
                                        Likely = "Somewhat likely",
                                        Likely = "Extremely likely")) %>% 
  mutate_at(vars(favor_humanitarian, favor_human_rights, favor_development),
            funs(bin = fct_recode(., 
                                  `Not favorable` = "Very unfavorable",
                                  `Not favorable` = "Unfavorable",
                                  `Not favorable` = "Neutral",
                                  Favorable = "Favorable",
                                  Favorable = "Very favorable")))
